---
title: "Introduction to gamestats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to gamestats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview of my package

The `gamestats` package provides tools for exploring, summarizing, and
visualizing video game data. It includes a built-in dataset of 20 popular
video games with ratings, genres, playtime, and more.

## How to do Installation

You can install the package directly from GitHub:

```{r install, eval = FALSE}
devtools::install_github("ygraham-code/gamestats")
```

## Loading the Package

```{r load}
library(gamestats)
```

## Exploring the Dataset

The `load_games()` function returns the full built-in dataset:

```{r load-games}
games <- load_games()
head(games)
```

The dataset contains 20 games with the following variables:

- **title** — name of the game
- **genre** — genre category
- **platform** — available platforms
- **rating** — Metacritic score out of 100
- **avg_playtime_hours** — average hours to complete
- **year_released** — year of release
- **developer** — game developer

## Finding Top Games

Use `top_games()` to find the highest rated games:

```{r top-rated}
top_games(5, by = "rating")
```

You can also rank by playtime:

```{r top-playtime}
top_games(5, by = "avg_playtime_hours")
```

## Genre Summary

The `genre_summary()` function groups games by genre and returns
average ratings, average playtime, and game counts:

```{r genre-summary}
genre_summary()
```

## Visualizing Ratings

The `plot_ratings()` function creates a bar chart of top games by rating:

```{r plot-ratings, fig.width=7, fig.height=5}
plot_ratings(10)
```

## Game Reports

The `game_report()` function creates an S3 object with details about
a specific game:

```{r game-report}
report <- game_report("Elden Ring")
print(report)
```

You can also use `summary()` for a shorter overview:

```{r game-summary}
summary(report)
```

## MY Conclusion

The `gamestats` package makes it easy to explore and visualize video game
data in R. Whether you want to find top rated games, compare genres, or
generate individual game reports, gamestats has you covered!
